Paper 1: Instrument development

### 2024-09-04 Rmd/Paper1.Rmd
Increased readability of document

---
title:        "Paper 1: Instrument development"
author:       "Niklas Karlsen, OsloMet, Norway, e-mail: niklaska@oslomet.no"
date:         "2024-09-03"
bibliography: "../data/meta_data/references.bib"
csl:          "../scripts/university-of-gothenburg-apa-7th-edition-swedish-legislations.csl" # (source: https://bookdown.org/yihui/rmarkdown-cookbook/bibliography.html)
output: 
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
    number_sections: true

@@

>>>>

---
title:        "Paper 1: Instrument development"
author:       "Niklas Karlsen, OsloMet, Norway, e-mail: niklaska@oslomet.no"
date:         "2024-09-04"
bibliography: "../data/meta_data/references.bib"
csl:          "../scripts/university-of-gothenburg-apa-7th-edition-swedish-legislations.csl" # (source: https://bookdown.org/yihui/rmarkdown-cookbook/bibliography.html)
output: 
  html_document:
    toc: true
    toc_depth: 4
    toc_float: true
    number_sections: true

@@

This document is large. This is mainly due to the analyses done in step 5: item reduction. Especially the scatterplots to check for linearity, checks for autocorrelation and multicollinearity, and checks of the normal distribution of residuals, produce a lot of output. They are provided here for transparency. Using the menu on the left, you can skip this part if you like.
